AIMS Data Platform R Client Notebook Example

### 2019-11-07 docs/10.25845/5c09bf93f315d/example-1.Rmd
Updates

Finally our filters might look like the following:

@@

Now the results have been stored in the `results` we can attempt to plot.

@@

Ok we have a plot, fairly unpleasant looking, that should be a line chart, also we should fix the time labels by putting the X values into an axis command:

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature")

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Davies Reef Platform Air Temperature in 2018", col='green')

@@

```{r}
results2 <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="January 2018", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Time", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations in 2018", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
legend("bottomright", c("Davies Reef", "Bramble Cay"), fill=c("green", "blue"))

>>>>

Finally our values and filters might look like the following:

@@

Now the results have been stored in the `results` object we can attempt to plot.

@@

Ok we have a plot, fairly unpleasant looking, that should be a line chart:

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature")

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature", main="Davies Reef Platform Air Temperature", col='green')

@@

```{r}
results2 <- getData('10.25845/5c09bf93f315d', apiKey=MY_API_KEY, filters=list('series'=87929, 'from-date'='2018-01-01', 'thru-date'='2018-01-10'))
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")

@@

```{r}
plot(results$dataFrame$time, results$dataFrame$qc_value, type='l', xlab="Date", ylab="Air Temperature", main="Air Temperature at AIMS Weather Stations", col='green')
lines(results2$dataFrame$time, results2$dataFrame$qc_value, col="blue")
legend("bottomright", c("Davies Reef", "Bramble Cay"), fill=c("green", "blue"))
